\documentclass[oneside]{book}

\input{common}


\SetOrganization{Primordial Machine's}
\SetLibraryName{Relational Functors Library}

\SetLibraryIncludeFileName{include.hpp}
\SetLibraryIncludesDirectoryPath{primordialmachine/relational-functors/\newline\$(PlatformTarget.toLower())/\$(Configuration.toLower())/includes}

\SetLibraryIncludeDirectiveFilePath{primordialmachine/relational\_functors/include.hpp}

\SetLibraryStaticLibrariesDirectoryPath{primordialmachine/relational-functors/\newline\$(PlatformTarget.toLower())/\$(Configuration.toLower())/libraries}
\SetLibraryStaticLibraryFileName{relational-functors.lib}

\SetLibraryVersion{v1.2}
\SetLibraryRepository{https://github.com/primordialmachine/relational-functors}
\SetAuthor{Michael Heilmann}
\SetEmail{michaelheilmann@primordialmachine.com}

\SetDocumentType{User Manual}

\begin{document}

\frontmatter

\begin{titlepage}
\maketitle
\end{titlepage}

\tableofcontents
\addtocontents{toc}{\protect\thispagestyle{empty}}
\pagenumbering{gobble}

\mainmatter

\chapter{Synopsis}
C++ 17 library providing relational functors.
The library is made available publicly on
\href{\GetLibraryRepository}{Github}
under the
\href{\GetLibraryRepository/blob/master/LICENSE}{MIT License}.

\chapter{Limitations and Restrictions}
The library officially only supports Visual Studio 2017 and Windows 10.

\chapter{Introductory example}
\textit{\color{orange}This library does not provide any examples yet.}
%Examples are located in the \href{\GetLibraryRepository/blob/master/examples}{examples} directory.

\include{building_visual_studio_2017}

\chapter{Library Interface Documentation}

\section{\texttt{namespace primordialmachine}}
The namespace this library is adding its declarations/definitions to.
The added namespace elements are documented below.

\input{binary_functor}

\section{\textit{concept BinaryFunctor}}

\subsection{\texttt{struct equal\_to\_functor}}
A \textit{BinaryFunctor} representing the binary expression
$\texttt{left\_operand} = \texttt{right\_operand}$
denoting wether the values are equal.\newline

\noindent{}This library provides specializations for \texttt{LEFT\_OPERAND} and \texttt{RIGHT\_OPERAND} being floating point types
and $=$ being the C++ built-in equal to operator \texttt{==}.

\subsection{\texttt{struct not\_equal\_to\_functor}}
A \textit{BinaryFunctor} representing the binary expression
$\texttt{left\_operand} \neq \texttt{right\_operand}$
denoting wether the values are not equal.\newline

\noindent{}This library provides specializations for \texttt{LEFT\_OPERAND} and \texttt{RIGHT\_OPERAND} being floating point types
and $\neq$ being the C++ built-in not equal to operator \texttt{!=}.

\subsection{\texttt{struct lower\_than\_functor}}
A \textit{BinaryFunctor} representing the binary expression
$\texttt{left\_operand} < \texttt{right\_operand}$
denoting wether the left value is smaller than the right value.\newline

\noindent{}This library provides specializations for \texttt{LEFT\_OPERAND} and \texttt{RIGHT\_OPERAND} being floating point types
and $<$ being the C++ built-in lower than operator \texttt{<}.

\subsection{\texttt{struct lower\_than\_or\_equal\_to\_functor}}
A \textit{BinaryFunctor} representing the binary expression
$\texttt{left\_operand} \leq \texttt{right\_operand}$
denoting wether the left value is lower than or equal to the right value.\newline

\noindent{}This library provides specializations for \texttt{LEFT\_OPERAND} and \texttt{RIGHT\_OPERAND} being floating point types
and $\leq$ being the C++ built-in lower than or equal to operator \texttt{<=}.

\subsection{\texttt{struct greater\_than\_functor}}
A \textit{BinaryFunctor} representing the binary expression
$\texttt{left\_operand} > \texttt{right\_operand}$
denoting wether the left value is greater than the right value.\newline

\noindent{}This library provides specializations for \texttt{LEFT\_OPERAND} and \texttt{RIGHT\_OPERAND} being floating point types
and $>$ being the C++ built-in greater than operator \texttt{>}.

\subsection{\texttt{struct greater\_than\_or\_equal\_to\_functor}}
A \textit{BinaryFunctor} representing the binary expression
$\texttt{left\_operand} \geq \texttt{right\_operand}$
denoting wether the left value is greater than or equal to.\newline

\noindent{}This library provides specializations for \texttt{LEFT\_OPERAND} and \texttt{RIGHT\_OPERAND} being floating point types
and $\geq$ being the C++ built-in greater than or equal to operator \texttt{>=}.

\end{document}
